DraftOne

### 2016-06-03 DraftOne.Rmd
Update DraftOne

# A function for continuous exposure which varies by season:
season_contexp <- function(n, mu, sd, trend){
  day <- c(1:n)
  if (trend=="cos1"){
    mu <- mu*(1+.6*cos(2*pi*(day/365)))
  }
  if (trend == "cos2"){
    mu <- mu*(1+.6*cos(2*pi*(day/365)) + ifelse(day<639 & day>274, .4*cos(2*(pi*(day/365))), 0))
  }
  if (trend == "cos3"){
    mu <- mu*(1+.75^(day/365)*.6*cos(2*pi*(day/365)))
  }
  if (trend == "linear"){
    mu <- mu* (1+ (day/n))
  }
  if (trend == "curvilinear"){
    mu <- mu*(1+day*(2/n)+day^2*(-1/n^2))
  }
  if (trend == "cos1linear"){
    mu <- mu*((1+(day/n)) *(1+.6*cos(2*pi*(day/365))))
  }
  if (trend == "cvd"){ #Figure this out later.
  } #else{
    #stop("Specify a trend variable from cos1, cos2, cos3, linear, curvilinear, cos1linear, or cvd."
    #)}
  contexp <- rnorm(n, mean=mu, sd=sd)
  return(contexp)
}
```

>>>>

# A function for continuous exposure which varies by season:
season_contexp
```
